Hydras \& Co.

### 2023-06-16 doc/chapter-fol.tex
small changes in documentation

Note that \texttt{freeVarF} is defined by cases over the basic connectives. In the following example, the connective \texttt{<->} is expanded into a conjunction of two implications, thus the 
list returned by \texttt{freeVarF} may contain redundancies.

@@

@@

\inputsnippets{FolExamples/substExample1}
\inputsnippets{FolExamples/substExample2}

@@

To fix this issue, we can associate  a measure (\emph{e.g.} a natural number) to each formula, such that the renaming of a strict subformula $F$ is strictly smaller that $F$.

@@

\begin{todo}
Motivate the induction principles based on depth. Compatible with term substitution and universal quantifier elimination.
\end{todo}

>>>>

\begin{remark}
  Note that \texttt{freeVarF} is defined by cases over the basic connectives. In the following example, the connective \texttt{<->} is expanded into a conjunction of two implications, thus the 
list returned by \texttt{freeVarF} may contain redundancies.

@@

\subsubsection{Closing a formula}
Function \texttt{freeVarF} is used in 
the  function \texttt{close}, which  universally quantifies  all the free variables of a formula.

\noindent From \href{../theories/html/hydras.Ackermann.folProp.html}{Ackermann.folProp}

\inputsnippets{folProp/closeDef}

\noindent From \href{../theories/html/hydras.MoreAck.FolExamples.html}{MoreAck.FolExamples}

\inputsnippets{FolExamples/closeExample}

% \subsubsection{Computing a fresh variable}

% It is easy to get a new variable, which

@@

\inputsnippets{FolExamples/substExample1}

Thus, the function (\texttt{fun f => substF L f i t}) doesn't commute with all \texttt{Formula}'s constructors.

\inputsnippets{FolExamples/substExample2}

@@

Thus, we cannot expect do define simply this operation by 
structural recursion over formulas. 
In~\cite{Goedel}, the approach is to define a \emph{measure}
which maps every formula to a natural number, then define substitution in such a way that the substitution of a term to a free variable in a strict sub-formula  of a formula $F$ is smaller
(w.r.t. this measure) than $F$. 
Then substitution could be defined by well-founded recursion.

Fortunately, such a measure : the \emph{depth} of a formula,
can be easily defined by structural recursion.

% To fix this issue, we can associate  a measure (\emph{e.g.} a natural number) to each formula, such that the renaming of a strict subformula $F$ is strictly smaller that $F$.

@@

% \begin{todo}
% Motivate the induction principles based on depth. Compatible with term substitution and universal quantifier elimination.
% \end{todo}
